Mining Scenario/Transaction Pairs in HW/SW Co-verification Using Symbolic Execution

### 2017-04-06 paper.tex
minor

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %                        Concurrency   
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
A co-design system is comprised of a set of concurrent FW and HW transactions 
which interleaves asynchronously. It is well recognized that concurrency is at
the heart of co-verification. The number of interleavings between the FW
and HW threads can be large, which can become a bottleneck in the
verification process.  
However, we observe that in practise that, industrial co-designs exhibits 
producer-consumer
relationship~\cite{polig2014micro,polig2014fpl,giefers2015accelerating} --
the master module (producer) solely updates the shared registers which are
consumed by the slave (consumer).  This key observation allows us to
sequentialize concurrent FW and HW models following specific interaction
patterns.  This drastically reduces the total number of interleavings 
between a FW and HW threads and simplies the overall complexity of the 
verification task. 
%
%===============================================================================
%\subsection{Contributions}
%===============================================================================
In this paper, we make the following contributions:
\begin{enumerate}

@@

  \item \textbf{Co-verification Tools:} We present an automatic HW/SW co-verification tool called, \hwcbmcv,
    which follows the monolithic verification technique.  Our path-based 
    approach is implemented in a tool called, \verifox. Both tools can handle
    co-designs where the hardware is implemented in Verilog RTL (IEEE
    SystemVerilog 2005 standards) and firmware is  
    specified in ANSI-C (C89, C99 standards).  We distribute the HW/SW 
    co-verification tools, \hwcbmcv and \verifox, along with our co-design 
    benchmarks in Verilog RTL and C models 
    here~\footnote{https://drive.google.com/folderview?id=0BynC6sd-wTYgWVQ4bXNtRDB5a2c\&usp=sharing}.

  \item \textbf{Property Specification Language:} We present an unified property
    specification language for co-verification that allows engineers to write meaningful 
     formal co-specification over hardware and firmware events and specify
     temporal correlation between these events.  Our tool also supports a
     fragment of IEEE Property Specification Language.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %                        Concurrency   
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
A co-design system is comprised of a set of concurrent FW and HW transactions 
which interleaves asynchronously. It is well recognized that concurrency is at
the heart of co-verification. The number of interleavings between the FW
and HW threads can be large, which can become a bottleneck in the
verification process.  
However, we observe that in practice, industrial co-designs exhibit 
producer-consumer
relationships~\cite{polig2014micro,polig2014fpl,giefers2015accelerating} --
the master module (producer) solely updates the shared registers which are
consumed by the slave (consumer).  This key observation allows us to
sequentialize concurrent FW and HW models \sjcmt{transactions instead of models?} that follow specific interaction
patterns.  This drastically reduces the total number of interleavings 
between a FW and HW threads and simplies the overall complexity of the 
verification task. 
%
%===============================================================================
%\subsection{Contributions}
%===============================================================================
In this paper, we make the following contributions:
\begin{enumerate}

@@

  \item \textbf{Co-verification Tools:} We present an automatic HW/SW co-verification tool called, \hwcbmcv,
    which follows the monolithic verification technique.  Our path-based 
    approach is implemented in a tool called, \verifox. Both tools can handle
    co-designs where the hardware is implemented in Verilog RTL (IEEE
    SystemVerilog 2005 standards) and the firmware is  
    specified in ANSI-C (C89, C99 standards).  We distribute the HW/SW 
    co-verification tools, \hwcbmcv and \verifox, along with our co-design 
    benchmarks in Verilog RTL and C models 
    here~\footnote{https://drive.google.com/folderview?id=0BynC6sd-wTYgWVQ4bXNtRDB5a2c\&usp=sharing}.

  \item \textbf{Property Specification Language:} We present a unified property
    specification language for co-verification that allows engineers to write meaningful 
     formal co-specification over hardware and firmware events and specify
     temporal correlations between these events.  Our tool also supports a
     fragment of IEEE Property Specification Language.
